Framing Effects in the Wild

### 2022-07-08 pres/Presentation.Rmd
allow caching to keep plot folder

knitr::opts_chunk$set(
  echo = FALSE, 
  message = F, 
  warning = F, 
  cache = F, 
  out.width="90%", 
  fig.height=8, 
  fig.width=15, 
  fig.align='center', 
  eval = T, 
  dev = "svg"
  )
# knitr::opts_knit$set(root.dir = 'C:/Users/nicol/Dropbox/PhD/Papers/Bild/github/bild')

>>>>

knitr::opts_chunk$set(
  echo = FALSE, 
  message = F, 
  warning = F, 
  cache = T, 
  out.width="90%", 
  fig.height=8, 
  fig.width=15, 
  fig.align='center', 
  eval = T, 
  dev = "svg"
  )
# knitr::opts_knit$set(root.dir = 'C:/Users/nicol/Dropbox/PhD/Papers/Bild/github/bild')
